\beginsong{Losing My Religion}[by={R.E.M.}]
\emptyv
\cseq{\[F] \[Dm] \[G] \[Am] \[Am/B] \[Am/C] \[Am/D] \[Am]}\\
\cseq{\[F] \[Dm] \[G] \[Am] \[G]}\\
\cl
\chordsoff
\num
\chordson
Oh, \[Am]life is bigger  \[Em]{   It's} bigger than you
And you are \[Am]{not me.} The lengths that I will\[Em]{ go to,}
The distance in your \[Am]eyes,   \[Em]{   Oh} no, I've said too \[Dm]much,
I've said en\[G]ough.
\fin
\num
That's me in the corner,
That's me in the spotlight
Losing my religion.
Trying to keep up with you.
And I don't know if I can do it.
Oh no, I've said too much,
I haven't said enough.
\fin
\averse
\chordson
I \[G]thought that I heard you \[F]laughing,
I \[Dm]thought that I \[G]heard you \[Am]sing.\[Am/B]       \[Am/C]       \[Am/D]
\[Am]{I  th}\[F]ink I thought I \[Dm]{saw } \[G]you \[Am]try.   \[G]
\cl
\num
Every whisper of every waking hour
I'm choosing my confessions,
Trying to keep an eye on you
Like a hurt lost and blinded fool, fool
Oh no, I've said too much,
I set it up.
\fin
\num
Consider this, consider this,
The hint of a century,
Consider this: the slip
That brought me to my knees failed.
What if all these fantasies
Come    flailing around?
Now I've said too much.
\fin
\averse
I thought that I heard \ldots{}
\cl
\freev
\chordson
But \[C]that was just a \[Dm]dream,
\[C]That was just a \[Dm]dream.
\cl
\chor
That's me in the corner \ldots{}
\cl
\averse
I thought that I heard \ldots{}
\cl
\freev
\chordson
But \[F]that was just a \[Dm]dream\[G],
\[Am]Try, \[Am/B]{cry,  } \[Am/C]{why,  } \[Am/D]try.   \[Am]
\[F]That was just a dream, \[Dm]{   j}\[G]ust a d\[Am]ream, just a d\[G]ream, dream.
\cl
\endsong


